R Notebook

### 2020-03-23 src/s_eight_schools.Rmd
added multivariate nonparametric test

full_data <- m_flattened
rand_samples <- sample(1:nrow(full_data), 0.7 * nrow(full_data))
training_data <- full_data[rand_samples, ]
testing_data <- full_data[-rand_samples, ]
gbmFit1 <- train(chain ~ ., data = training_data, 
                 method = "gbm",
                 trControl = trainControl(method = 'none'), 
                    tuneGrid = caretGrid, verbose=FALSE)

plda <- predict(object=gbmFit1, newdata=testing_data)
tibble(predicted=plda, actual=testing_data$chain) %>% 
  mutate(correct=if_else(predicted==actual, 1, 0)) %>% 
  summarise(mean(correct))
varImp(gbmFit1)

plda <- predict(object=gbmFit1, newdata=testing_data, type = "prob")

nsim <- 1000
mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
mAccuracy_centered <- mAccuracy

full_data <- rstan::extract(fit_ncp, permuted=F)
k <- 1
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = (nparams+1))
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:nparams] <- full_data[j, i, ]
    m_flattened[k, (nparams+1)] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V20) %>% 
  mutate(chain=as.factor(chain))

full_data <- m_flattened
rand_samples <- sample(1:nrow(full_data), 0.7 * nrow(full_data))
training_data <- full_data[rand_samples, ]
testing_data <- full_data[-rand_samples, ]
gbmFit1 <- train(chain ~ ., data = training_data, 
                 method = "gbm",
                 trControl = trainControl(method = 'none'), 
                    tuneGrid = caretGrid, verbose=FALSE)

plda <- predict(object=gbmFit1, newdata=testing_data)
tibble(predicted=plda, actual=testing_data$chain) %>% 
  mutate(correct=if_else(predicted==actual, 1, 0)) %>% 
  summarise(mean(correct))
varImp(gbmFit1)

plda <- predict(object=gbmFit1, newdata=testing_data, type = "prob")

mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
mAccuracy_noncentered <- mAccuracy
```

```{r}
d_df <- tibble(centered=colMeans(mAccuracy_centered)/(1/n_distinct(training_data$chain)),
       non_centered=colMeans(mAccuracy_noncentered)/(1/n_distinct(training_data$chain)))
```

Plot two R* distributions
```{r}
g1 <- 
  c_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  xlim(0.78, 1.6) +
  scale_fill_grey("Series", labels=c("centered", "non-centered")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("A.") +
  theme(text = element_text(size=14, colour="black"),
        legend.position = "none")
g2 <- 
  d_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  scale_fill_grey("Series", labels=c("centered", "non-centered")) +
  xlim(0.78, 1.6) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("B.") +
  theme(text = element_text(size=14, colour="black"))
a_df <- readRDS("../output/eight_schools_replicates_4_index.rds")

pdf("../output/eight_schools.pdf", width = 12, height = 6)
multiplot(g1, g2, cols = 2)
dev.off()
```
```

>>>>

both <- f_fit_gbm_predict(m_flattened)

nsim <- 1000
r_star_centered <- f_r_star_distribution(nsim, plda, testing_data)

# noncentered
full_data <- rstan::extract(fit_ncp, permuted=F)
k <- 1
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = (nparams+1))
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:nparams] <- full_data[j, i, ]
    m_flattened[k, (nparams+1)] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V20) %>% 
  mutate(chain=as.factor(chain))
both <- f_fit_gbm_predict(m_flattened)
plda <- both$predicted_prob
testing_data <- both$testing_data

```{r}
d_df <- tibble(centered=r_star_centered,
               non_centered=r_star_noncentered)
```

Plot two R* distributions
```{r}
g1 <- 
  c_df %>% 
  melt(id.vars=NULL) %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  xlim(0.78, 1.6) +
  scale_fill_grey("Series", labels=c("centered", "non-centered")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("A.") +
  theme(text = element_text(size=14, colour="black"),
        legend.position = "none")
g2 <- 
  d_df %>% 
  melt(id.vars=NULL) %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  scale_fill_grey("Series", labels=c("centered", "non-centered")) +
  xlim(0.78, 1.6) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("B.") +
  theme(text = element_text(size=14, colour="black"))
# a_df <- readRDS("../output/eight_schools_replicates_4_index.rds")

# pdf("../output/eight_schools.pdf", width = 12, height = 6)
# multiplot(g1, g2, cols = 2)
# dev.off()
```

# Plot tau prediction accuracy across quantiles
```{r}
full_data_all <- rstan::extract(fit_cp, permuted=F)
full_data <- array(dim=c(500, 8, 11))
k <- 1
for(i in 1:4){
  first_half <- full_data_all[1:500, i, ]
  second_half <- full_data_all[501:1000, i, ]
  full_data[, k, ] <- first_half
  k <- k + 1
  full_data[, k, ] <- second_half
  k <- k + 1
}

f_r_star_accuracy <- function(nsim, pred_test_prob, testing_data){

  mAccuracy <- matrix(nrow = nrow(pred_test_prob),
                    ncol = nsim)
  for(j in 1:nrow(pred_test_prob)){
    test <- apply(rmultinom(nsim, 1, prob = pred_test_prob[j, ]), 2, function(x) which(x==1))
    mAccuracy[j, ] <- if_else(test==testing_data$chain[j], 1, 0)
  }
  return(mAccuracy)
}

nsim <- 20
mAccuracy <- f_r_star_accuracy(nsim, plda, testing_data)
colnames(testing_data) <- c("mu", "tau",
                            "theta.1", "theta.2",
                            "theta.3", "theta.4",
                            "theta.5", "theta.6",
                            "theta.7", "theta.8",
                            "lp", "chain")
colnames(mAccuracy) <- map_chr(seq(1, nsim, 1), ~paste0("V", .))
mAccuracy <- mAccuracy %>% 
  as.data.frame() %>% 
  bind_cols(testing_data)

lbreaks <- quantile(mAccuracy$tau, seq(0, 1, 0.1))
mAccuracy$tau_cuts <- cut(mAccuracy$tau, breaks=lbreaks, include.lowest = T, right=T, ordered_result = T)
cuts <- sort(unique(mAccuracy$tau_cuts))
r_star <- matrix(ncol = length(cuts),
                 nrow=nsim)
for(i in seq_along(cuts)){
  temp <- mAccuracy %>% 
    filter(tau_cuts==cuts[i])
  r_star[, i] <- colMeans(temp[, 1:nsim]) * n_distinct(testing_data$chain)
}
colnames(r_star) <- seq(0.1, 1, 0.1)
r_mean <- 
  r_star %>% 
  melt(id.vars=NULL) %>%  
  group_by(Var2) %>% 
  summarise(value=mean(value))
r_full <- 
  r_star %>%
  melt(id.vars=NULL) %>%
  bind_rows(r_mean) %>% 
  mutate(variable=as.numeric(as.character(Var2)))

ggplot(filter(r_full, !is.na(Var1)),
       aes(x=variable, y=value)) +
  geom_jitter(height = 0, width = 0.02, colour="grey") +
  ylab(TeX("$R*$")) +
  xlab("Quantile") +
  geom_hline(yintercept = 1, linetype=2) +
  theme(text = element_text(colour="black",
                            size=12)) +
  geom_line(data=filter(r_full, is.na(Var1)))
```
